Wolfram Lanauge interop with Wolframite - DRAFT

### 2024-01-28 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).

::: {.sourceClojure}
```clojure
(ns index
  (:refer-clojure
   ;; Exclude symbols also used by Wolfram:
   :exclude [Byte Character Integer Number Short String Thread])
  (:require
   [wolframite.core :as wl :refer [wl]]
   [wolframite.tools.hiccup]
   [wolframite.base.parse :as parse]
   [wolframite.jlink]
   [scicloj.kindly.v4.kind :as kind]
   [scicloj.kindly.v4.api :as kindly])
  (:import (com.wolfram.jlink MathCanvas KernelLink)
           (java.awt Color Frame)
           (java.awt.event WindowAdapter ActionEvent)))
```
:::

@@

::: {.sourceClojure}
```clojure
(wl/eval '(Dot [1 2 3] [4 5 6]))
```
:::

@@

::: {.sourceClojure}
```clojure
(wl/clj-intern 'Plus {})
```
:::

::: {.printedClojure}
```clojure
#'index/Plus

a simpler way to do the same -> fn Plus in this ns

::: {.sourceClojure}
```clojure
(map wl/clj-intern ['Dot 'Plus])
```
:::

::: {.printedClojure}
```clojure
(#'index/Dot #'index/Plus)

 Call interned Wl functions:

::: {.sourceClojure}
```clojure
(Dot [1 2 3] [4 5 6])
```
:::

::: {.sourceClojure}
```clojure
(Plus 1 2 3)
```
:::

::: {.sourceClojure}
```clojure
(Plus [1 2] [3 4])
```
:::

::: {.printedClojure}
```clojure
[4 6]

@@

### A helper function to view things in tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly)

::: {.sourceClojure}
```clojure
(defn view
  ([form]
   (view form nil))
  ([form {:keys [folded?]}]
   (-> form
       (wolframite.tools.hiccup/view* folded?)
       kind/hiccup)))
```
:::

 ### Draw Something!

@@

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhgwArAPdXABUVFTc3N4CAgAMDAxAQEFVVVZCQkK2trRwcHJeXl3p6ekZGRggICAcHB/X19URERC8vL4+Pj/39/ZKSkllZWcrKypycnP7+/vb29lhYWIyMjE5OTlJSUtvb246Ojri4uJSUlKenp5OTk29vb8XFxYiIiGtra8jIyKqqqtfX14qKiu7u7vT09LKysh0dHVZWVqOjoz4+PuDg4OHh4b6+vry8vGlpaezs7EVFRcTExL29vfLy8rq6uoSEhF1dXaioqJqamjU1NXh4eDQ0NJ+fn19fX5aWlqWlpfr6+tXV1W1tbd/f36urq5ubm7W1tYmJifj4+H9/f6GhoVRUVJ2dndnZ2R4eHv///8vLywAAAMfHx2RkZPv7+9DQ0JmZmbS0tNTU1OLi4kdHR+vr683NzXNzc6ysrElJSYKCgsPDw7GxsaamplBQUHx8fDExMXl5eUhISK6urujo6N3d3Q8PD3R0dOXl5dPT02FhYVxcXOPj49zc3H5+fjIyMufn58DAwGJiYvz8/DY2NsbGxpGRkXFxcZiYmLCwsHd3dwQEBEpKSrOzs9HR0cLCwp6eng4ODubm5s7OzlFRUfDw8IGBgfPz82VlZYeHh4aGhjg4OAEBAUxMTAYGBmdnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAgwArAAAI/wCvCBxIsKDBgwgTKlzI0CCShhAjSpxIsaLEFTFyWNzIsaPHiUReMCnUY9LHkyhTTqzB5sjAP1OkqJxJc2YVJSVYGITBgUbNiGCyHCrIZsjPkxhUmEiRcAemER2OLgw6lGBRqR1DbODRMIkNDVCwHqRK1KhYimkyUJn4YdOPswTJWjULt6GMOpRuWLRAgURduQOv1l0oYcKWLh3HREEU5mzQLJAjZ6E7+GAcMS1QkgEkQmzQMmZChw5CufJALEWM0FSDo+rPoGbKmiYop80bO0dB4CHzOkvsubMFeslzQqweRHz20IQt23QgQUwGD3LzZCZz4JXvWCI029CmDymvB/+mrGiR1Ek9Cs0JfgWKBhtJ6l4gZIlRTSlT/rAn2GEEph11LVEGGjOkRAMHMOx30IEJ1tWIFY581N9/CiaEn351wSCJDhu5B1+FC6GnXl2VXDJCJQRBkskjmnDiQgQHofAdiBDd0UkEXNSVRCQDrZGIJhAU8QAdWQhSUBRA0DiRE2f8NpgDDTCgxUASLJCFEAStoGRFhvhQXF0vZGGIQY8ksqVHfrShAG5nWcHAQZ1kUcGZHlVQRAJnMYDAQY5kgQmdHx0AxxdY6XnQEVmUAehHgRgA3lFuHmRDFg0u6pFJRxWQRRMGETCABJaGKhCUDMw5kCJZCCDqqj5q0scWihAmkEUAq9aqIouJAOBBrbz26uuvwAYr7LDEFmvsscgmq+yyzDYLYkAAOw==" style="margin-top:1rem;" /></div></details></div></div>

@@

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhYwAqAPdeAPHx8dvb29/f3+7u7tra2rqvoquej+bi3ZuLebuwpOjk4JWEcfDu7N/a1ZiHdZ2OfKudjrGklo58Z8zEu+np6d3Y0dnTzM3FvINwWdPMxNDIwPf29O7r6M/Iv8O5r+rn4/X08srBuLCjlY99adXOx66hkqCRgIJuV9bPyIVxW8/Hv/7+/oFtVuTg29zW0LWqnKyfkJqKeN/a1OTk5NvVz5uMeoVyXPr5+MG4rZF/a417Ztzc3L+1qZB+aq+ilNPNxY9+afX19Yt5ZIZzXePe2fn5+fr6+tnZ2eXl5YRxW6eZiresn/Lw7pmJdrarnvLy8ol3YYh1X8K4rdHKwtDJwce+tLyypvT09O3t7dTNxbKmmOPf2ritoIl2Yf////b29vv7+6WXhuDb1YFtV+fn59bQyfz8/O3q55+QfuHc1+Le2aqdjt3d3ejo6PDw8PPz8760qPTz8fDu68jAturn5O3r6Obm5vr6+aGSgbSpm/j4+H9rVJmJd4d0X4JuWIp4Y6GSgrWpnP39/fv6+svDuo17Z5aGc6KUg6OVhPb19JaFcoRwWunl4d7Z0/f399jSy9XPx4d0XpKAbevo5Ovr69zX0eLd2LmuofPy8Me/tefk38W8sYNvWaKTgufj3/39/NnTzbqvo+Dg4LSomqaYiJKBbaeZifn496+jlMC2q97e3uXh3IBsVZWFcpyNe9LLw5SDcPj39tHKwZOCbrernuPj48rCueHd1+/t6u7s6baqnfb185eHdJyMetTOxuzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5iH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAYwAqAAAI/wC9CBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxZsMibJyhTqlzJsqXLlyivgCGpMIiqIzhz6tzJs6fPnzxrGaFpMMgRMkVWEE244ouoHWaWDlRlRypDQaraWDVyRI9VhlhUWb1yRNDXhW+OKF1Kdu1ZhG2lxn0LV+1BJlQO7TmDUAyrQAS17Bk8GHDBuXQNIibIQweUvQdv5LBhWOAaNDQy06Cj2G7izm4NyoBs0EmMMJW9HHqxcPFnga4JjuZbMM2YFnhSx8DR2i6LKUC6uFiSQolZL3Jg9EkCqAXBQaEK+TE0haDwMooWGWpE8BWfIUMQPf8iGHvg7IJ3JF3ygia1pF6SosR4dTAui1KTfAzJZIkVDS+Y6AALFZAAwskWAq3QSSRVgDLKHpkM1EUMpGhShylRnCJQJaykskojcLQSy0DlCXQeQVzMMgh7qaFCSyO36LLHJqB5wYItXrxSikB/zOFFHpHsIpAgvLgikC97cCeQLikkIlAXpKz1yx6VCCTFEJ/UFVpBJwqkxglECNReQiVAsaV9snhBQhMC6UDjCCIQFMIeIHjhQw8EfbAHCk96MNAne3QgEAdCNKGBkId5dlCXg8wSykBjIpTBHpgkqhQLaa7ZJo0Y8EDQI3t84AUiaBAUyx4h9EnQHhcMlEgqhoz/YYIF5CkqGmlqEqbrHhUcNMEeG1hqY6ZseuGmFxJEQJAte8ThRQk5EETHHiSoOhCrBuUiY5qw2colrht4Iq64TUDgiYaM1DHQCg84UCOmahZ7rC5ROOnFCk08IBAKezQwEBdBWisQtl4wcJxAfPhAordegJBGGnPs8UMalhwUqRcJDGEFDVmYcNu7xG7qxQY6LCALCp1wosBAYfSRCSiB7EGIhH5e26oXCCiiwgEHeMDCDwtvmeuunFhc2QpU9DLEIodoUp9vIRtLoxe4GLAcHggOdEcBOkxHhXU1D3zzBjg4kEQkNdAXtFwMf1YiSG+/FbdHc39VN0d3sy20SI4cVTHUawS5sYNVKxAwAOAEzTDDV1gQ8AbiK1ByhCNfrUDBEQIgofnmnHfu+eegh775DGwEAABdjmBhh+ist+46EmQMMBPitNdu++2456777rz37jtIAQEAOw==" style="margin-top:1rem;" /></div></details></div></div>

>>>>

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
Note that to use Wolframite, you need Wolfamite in the dependencies,
as well as the `WOLFRAM_INSTALL_PATH`
set up in your system, as explained in
[Wolframite's README](https://github.com/scicloj/wolframite/).

::: {.sourceClojure}
```clojure
(ns index
  (:refer-clojure
   ;; Exclude symbols also used by Wolfram:
   :exclude [Byte Character Integer Number Short String Thread])
  (:require
   [wolframite.core :as wl]
   [wolframite.tools.hiccup :refer [view]]
   [wolframite.base.parse :as parse]
   [wolframite.jlink]
   [scicloj.kindly.v4.kind :as kind]
   [scicloj.kindly.v4.api :as kindly])
  (:import (com.wolfram.jlink MathCanvas KernelLink)
           (java.awt Color Frame)
           (java.awt.event WindowAdapter ActionEvent)))
```
:::

## Make sure Wo

@@

::: {.sourceClojure}
```clojure
^:note-to-test/skip

(wl/eval '(Dot [1 2 3] [4 5 6]))
```
:::

@@

@@

@@

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhBgFVAPdkADAwMLq6uiwsLNPT0x4eHo+Pj9/f31VVVYyMjICAgFtbW0pKSi8vL3l5eZmZmba2ticnJ3FxcZiYmNfX18jIyLOzs2dnZ+rq6j8/P3x8fHp6eo2Njfn5+aurqyYmJoODgz4+Ps/Pz0dHR9bW1uTk5FxcXKqqqsbGxkFBQdHR0WVlZYeHh0lJSYKCgu7u7m9vbxMTE6+vr/b29lpaWsXFxVFRUZqamjU1NSgoKLy8vNnZ2U9PTwkJCVJSUiEhIV5eXqenp+Dg4MzMzFdXV3t7e5aWll9fXxUVFf39/Q0NDVZWVtra2qysrIqKir6+vuHh4RAQEPT09BcXF+3t7R0dHbKysjo6OhsbG8LCwisrK9LS0gAAAAwMDKOjoyoqKjs7Ow8PD+Xl5XR0dMvLy/////X19UREREJCQkNDQ6SkpFNTU+np6TExMcnJyYaGhjg4OP7+/qGhoX9/f/j4+Pf393BwcGtrawsLC4iIiOPj4wEBAWxsbLe3twcHBxoaGi0tLRwcHAMDAwgICMPDw7GxsRYWFqampnV1dejo6N3d3a6urkhISDMzM2pqar+/v+vr6wICAjIyMsDAwGJiYufn5/z8/FhYWAoKCvPz8/Dw8F1dXaioqCUlJWBgYKCgoMfHx/v7+2RkZGZmZjk5Ofr6+qWlpZGRkQUFBc7Ozg4ODubm5ikpKVRUVJ2dnWlpae/v7wYGBkxMTCAgIEZGRvHx8VlZWZKSkk5OTq2trSQkJBERESIiIh8fH7m5uWFhYTQ0NJ+fn3h4eLW1tZubm4mJiU1NTX5+fi4uLpycnMrKyqKiotjY2BgYGDc3N97e3uzs7EVFRSMjI+Li4hQUFLS0tNTU1I6Ojri4uJSUlBISEtXV1bu7u21tbfLy8ktLSwQEBLCwsHd3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3dyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAABgFVAAAI/wDJCBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJEmOvKSVTqlzJsmXFKGK2FHLksqbNmzg9wklzZQsaWVvUOMtJtKjRowLbvNliZQyZOU2S9CGCCanVq1g9qjKyBZAhOAQpTdLjpwuSrGjTqlVIxw0XQXKiIBTyZcubNmvz6r0KR5GPLUOCLIQDBNCWH2H2Kl7sUsuZLWywPCwjh8cdN3QYc8zDhIlThUE6C9F89FEjSIWQVZL4xNIWH4rAkr64acuWTgs92Q41OycpU1BOiclkEUukLWe09K5Y+3bu3cttXlu1pdiSjJVaFYLk6lH0iM1xK//UvYX395VLYm3x0qsjrUOnoJgidb5h+Ofl65fMJCa+LfofLXHLFqtco59C940H3YEgVYLMdnY8Q1IvXmwRy3UMFpRgQuSZlyFHgxyHhnIpkWKLLsIR9yEZGyLU4YoaPTHEFruAI9tKz9iBmmoftnjQizBaRJkgXOAxx01aoLFFJINk6KNBQAYpERyGGOaLKkTBAc4ugD1xYHOLSCLmmGRKEsyCUkJEF1OfGTUHHlzwIEcZ9TVn25145plfmg5R4oseXt2IlCq+bEEFEILOZqeejO7Jp0JzEJOEIMbIlVYyo2zxxWjLNdeMJ6CGKqonoaD5qEFwEBINYILlBUcpgOj/MQklvTVnCX4enkpQNdBAJtliURgjSBJNHKmZrbjqStAUewSS2mqkBaHEFrlUkWheyCro6KmgYJNNit9hwcYWs2izWLYcmsrnNllUh+F5lQxzRCDcoKQXui6qG6QkXBb4IX+nJDGEsWrh+6O+H3YTzjd6hAPgijoAlUUOaxkMJcIHIgEMM5A0MhSfuOCwRQ2JpGVxQVF+SMMvyJF46m9QwBJMN1mdTFDKA2Giibm95THDazFc++gjrkDCjCdnWWXzQDgnBUMgL7igmQwtXHLHCpkpa1AKKGxxwwkfuvDCNzAUAcpecJjAyxZGJKY1Qn39VQIJH44gwhZ/OJFXCCDY/4XX2wu1dcclH8iQIRzUeLBFDx9jtYYKZKWRNOAMhfHDFrx0IHR0HGwARh8a0GJV56n0kUFVlEPURjNbYBDChxdYoMc3GkyekzCKs9J46hAh0YUfkIhywYcV6LJFMxTkNAELWxxDE+8VYZJBH2BYw8HhHayNWE2v1PHNNBJAC71FzrCyBQQPfCjDB1Zj9hAih7wRDTOcvNHAGhBVIsE030TwyvgbkQQDtrCAZXwoDwp4TWwWIgRONGoLHkBFQxwxwEVMAIAdqYQD+Oc/lbEMDVk7iCj0pAc9uUIhcKgFBIWBQZC8IgLfc4D49KMxOySEebYJxAL4cD06gMMMkLhTMf8UkgAEXK+FIVneFhggCV0Z4044wJ9BpPEX2+ABiTgRBgS2cAAD8MkZJVySQpAgsi1AAhFYvAkHrAEGQWTAUjBS0hbuEEKE0KIPttlBGnESOz1cIQ2b+w4HgriFAjTkTFv4hu326JIQYGALo0jGh1phmz44BBSBsE0VGIkTOGTvNlg60Cxsw4aHrGoLt+IkTtZ3CS5gTT+5sM0eHuIavKmSKCQoAY2Cdh4p2MYaDwmHbQhwy6Kc4AY+GcB3UmEbZTzEGraBQTGLgoQ4cCxCyymEbRDwkAzYBhDTNEo3GgALXXyiN7HcwiwdwpUlhvMoiQgFnWZjBttE4iEV2sIt3smsT4XYoJIOQcIpNNnPghqEDmG0RUMSYJtTGPShBOnbFrhwxIRggge28QZEN6qDMN5gIe1KpOg2ClFh2kYA9iqIKk65hQyQlKSPsc03biGJsyAhACwgJGBe+tLL5UmndyoBT3lKgyoyahcBGKpSpfECRsjiCAQAwAsuqNSqWvWqWM2qVrfK1a569atgDatYx0rWspr1rGhNq1rXyta2uvWtcI2rXOdK17ra1a0BAQA7" style="margin-top:1rem;" /></div></details></div></div>

@@

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhxgBTAPeXAPHx8fb185F/a6iaivHv7O/v7/Hv7eLd2KKTgt/a1YVyXMW8scW8ssrBuPf29O7r6OPj4+Hd18rCuYh1X9/a1L+1qYt4Y7Gkluvo5Orn5LOnmaSWhtzX0d3Y0tXOx5iIdol3Yfn5+JKAbeDc1uHh4Z2OfO/s6se+tPv7+p6Offb19KWXh5eHdIFtV7muoqaYiNPMxLerntDIwINwWaudjpaGc5SDb7KmmNTNxYRwWrCklq6hksK4rcnAt4d0XoNvWbqvoqCRgIJuV+Hc187Gvd/f36OUhNnTzI9+adPNxcvDue3q58/Iv6yfkN7e3uXh3Ozs7Id0X4JuWMzEu72zp5GAbOTg26ibi6GSgpuLeZ+Qfsa9s+Db1aWXhuLi4tvb25+Qf/T09IRxW+Xl5ZWFcoBsVfDu68G3rPTz8cjAtubm5unm4vr6+eTk5NvVz9zc3I17ZuLe2ambjKqdjpmJd+rq6u/t6raqne7s6djSy/f39+Xh3aOVhIp3Ytra2tnZ2Y99abCjlfPx7/v7+7qvo7SomuDg4O7u7tbPyIVxW/X19cO6r/r6+vLy8rOnmpeGdPj4+Ih1YNfRyc/Hv/7+/rGll4l2Yf////b29ujo6N3d3ePe2dbQyefn5/z8/Ip4Y6qcjfDw8L60qPPz89DJwc7HvtfRytHKwvr5+PXz8paFcpiHdezp5sS7sMe/tdvWz+fk37uwpMC2q9TOxpyMesvDuo17Z+jk4JWEcfDu7IZzXYt5ZNHKwZOCbrWpnPz8+/39/fv6+sS7sc3FvK6ik6eZiZKBbZOCb/j39pSDcNLLw/39/Ofj3/Py8LmuodrVzpqKePf29Y58Z+bj3uzq5unl4d7Z07Spm6GSgZB/a7arnpmJdu3t7Y58aOvo5enp6d3Y0ejl4Z2NfMi/tdrUzdXPx39rVPTy8K2gkritoIx6Zfn4962gkb2ypoFtVqeZivLw7resn6+ilJB+aubi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3SH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAxgBTAAAI/wAvCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0g3AmtUR82Yp1CjSp1KtarVq1izapWaiRukpBQHffPzp6zZs2jTql3Ltq3bt3DdGgoDFqKiN3Hz6t3Lt6/aTpTqMsRE9o+mUIwCC57oSVEns2MWJ/SE908nYJIxjqp8KLPBOmU7ec6oh+wXT6MFUvpiGHXqi1DKdk4dRvZrjKv/eHnNrezX2xfb/Pny+ltZ18ArPv6DeXSmss2TU3zOPDX16NIlXrcOPfv07s7Be/+PuD189fHkxWcuj/4h+/Xq2zN8L5m+fIX2Hf46daXYNImU3FFMMa8kVMmACCY4YIEL5XffQQ4iBIwVUzQRhTkYuiERFRiao0RCunQooogfNhjfgwhFeNASI2YY0RFldFiiQcDECIcROOaYIznznYiiQSoaBE8XRHZRhYsPLXHhHBjOWBAaGKZjUZA/UplQO0g2hIoq5iSzRpMIsYJhK1P6+CNBViKEpTkaOtSEOVLAAguYB22CIRNlnneJKLHg4YksuNgCSi6XUOLKI7vwUQ1CwQxTjDGfHDOHMsswxIwz0MAhDS3tUJPQFrFYIxAbw2CRzS7bxCKIQvAIY2Qf3WT/kQ44iqVoZkNrtsnQOBimcYmdHiL0TJYTsZeIOeW82eEqlBQioiXnGESOOi2aU8UmCa3DTowjunMHcgT1Yk48v87TYiT0IJSGGNVaS0StBaV5UK4NDSGEOegINASdBp2C4X8VGWuOOObQQkgyGGpjThBAmGuOKAVNwi00Z9QiCpfm/PDMQcg8gqEPlfTgyg45YIgNuAKJ2wQO99bgCxU0zIChMShfIgOGusQAAzh5jPNCC+a4s4etekpE70LwUMsCG/ryW1AaGHrDyw1drBBIGna4J96x5lwRmArsmhODQNTEmAJBe0hhjhC8EETJCTH6YIJBcmAIRjMEmeCx2AaJ/2uJO32YQhArn2CYh0HZwOmNkDoskpC8Bh09WQnmRDJ308EeJAuGP7RYxg4qNCSwD2gMFIQ52aAwUOLzEHS6OVMcJAqGxBQ0AoYihGBQMyCY04Kn4c5MaEGuYEguQchg+EGxtzIkOUIKl8EBQftmbtDs5nxSiStT8LABt6qEbqKexxpBECjmaEAQNObsMlAGGJKB0C+FuyO+QEya4wFCJ0RZkLhSwJtBxGSODRQEGCESAwa007yFPM8gysCQ46jnNLeNoxa/KEg1xGWOC/SIfOYw30BokD6CZMEcFhjIFjDEg4RcA0MwGAglLiSGSh3kHBjqxf/MkQhGYagEBlkhD/+dsTitFS0iDyRIONglB4NUz0kOMcOx3JGK8UWnfAQhofoGcsIUCuQGxCpIKTBUgYHAA0NZUEg3zFEGeImrhwhB40G20DkM4SIWFKgZkBqokCQKJBpHmoAbhkDIQkoAQy4g5C0g4ggMJcGKA8HiCEvIRRQO5AoYekJC8oAhXwwkHBjqgkI+gKEqDuSNCZHjQR5QCEuIyAc6SNfj+HilMA6kAe1qVxofQgQMMQCSApGkQLRoQksKhB0YikBCZoHIgbDIHFhQCMLMobtT8jCV5tilhLhACBaIaA7RIBp2kGhLgfQgl9XSZkNIgaEFAPMSwrwEMSvpxUs4A0OnSIgwfDn/kORZKyEINIcCdgjHg6iSISYQhQ9+CK+BQK4gfizUMiZK0YomAEMNmOg4F0IIGL4znvMUSBcHIgkMBSIhCMCQFQiyt6wd5AAYMmDwCmqQgzYkF4BIJoRoqaZyMuSJB0GFAbJFrRaYcpYgFOEwKSlSY15iHQkkwEGYESMkwGtz5rgDQgaAoVIQFJvqbMgZMNS2PR4RIhFdCFANIo9dgOMgKHgH7T54xRBmkamXGOlAsFqCag4kFdP0KkGiMQE2csIguDSHAGxoTZoWxKaXwAMdRIWQupkjDjs9a0KsIInOdhZ9D/OsJI7gkLXmjWsv8IApHaAMG2AIEKX7qF0nucWm/9bzEr+gBYaSkYcMsgEGSMDQOxp6CVPEqAXOuBwGbhCjH2Drq3HMZkEItjAPBIAg57gDhrZB3EvIy7LovGa9KiiQW3izQz+IArfMgYsHiG5rs11qbfPqVIGkQgsdcscE1nsFvxaEFDLDkALCZo4obKxv4jWodAmyhpRiqAzSYEEWBMCtbLg3sxtNCHjR6diEmLYglFAGFoAmImm0QnXvTepd56tXgixDCYkTERmU0d2BeIMGauuQGG4wPAR3eCCQFcg0KkGtEcFBFOtAaoZp4gBr8GIYHshAejRrEQwgggiSwMNDQtABUpyCCygOiTfcQIpSSMIbNXYoT4nyUPS0Gdkob/ZOnH0yZ+nUmSd3Bk6edbLn1/QZJ382z5LBApo/DOJMClFDWdKclEOURRGITggJDPMaSJTlG5E+yCDKoobbOKEsesh0QYTzh0bcBgBlKcKgH1SAshgiORAoiyYgHWlPLMcPmEiOJ4pgFghwAwCNCLawh03sYhv72MhOtrKXzWxih+IblflDKLIDDEX75drYzjZf3kCX8WBiDIXRtrjHne0icGPVtwGGHsLQ7Ha7+93wbvcoMMEIUdv73vjOt773ze9++/vfAA+4wAdO8IIb/OAIT7jCAx4QADs=" style="margin-top:1rem;" /></div></details></div></div>
